### 2021-06-18 letter/responseLetter.tex

\vspace{0.2cm}

\item In the second place, I would recommend to include more details on the experiments conducted. This is especially 
true for the second study, where Section 3.3 is a bit shallow. The three steps of the methodology are indeed shortly 
described without providing enough details, hence possibly precluding verifiability and replicability. In addition, the 
methodology is not linked to the research questions: I would recommend to restructure Section 3 in order to have 
data extraction processes and data analysis procedures for each research question.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for raising these issues. We reviewed Section 3 in full,
to detail our approach better. In particular, we expanded the methodology of our
second study (Section 3.3) and highlighted our data collection and analysis procedures.
Regarding verifiability and replicability, we improved the documentation of our
packages and tools (see the next comment).}

@@

\vspace{0.2cm}

\item The proposed DroidXP benchmark seems not to be available, which is a pity since it might be very useful for other 
researchers. I believe the paper may have a stronger impact if the tool would be available. The same is true for the 
data and scripts used for the experiments. I would appreciate if the paper may have an online repository making all 
data and tools available.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for this comment. All tools, datasets, and scripts we used in our research are available on-line. The following repositories present detailed instructions about these assets:

  \begin{itemize}
    \item \href{https://github.com/droidxp/benchmark}{DroidXP GitHub repository}.
    \item \href{https://htmlpreview.github.io/?https://github.com/droidxp/paper-replication-package/blob/master/replication.html}{Datasets and scripts}
  \end{itemize}

@@

  \vspace{0.2cm}

  We also included references to these repositories in the first section (Introduction) of the current version of
  our paper.}

@@

\begin{itemize}

\item The abstract is not clear. First, the context if not well addressed.
  For example, why ``mining Android sandboxes'' is important? I had to read
  several related reference at the beginning to understand it. Second, it is not common practice to 
include reference in abstract. However, I reserve my opinion since I know it may be preferred by some researchers.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} Thanks for raising these questions. We reviewed the abstract
  to better explain the relevance of the mining sandbox approach. Literature reports
  show that the mining sandbox approach is effective  not only to prevent malicious
  calls to sensitive APIs but also to classify a version of an app as a malware.}

@@

\vspace{0.2cm}

\item By definition, mining sandboxes means a technique to confine an application to resources accessed during automatic 
testing~\cite{jamrozikZ16}. But in 3.3, you are comparing the source-sink pairs between that of a benign app and its malign twin. It is already not ``Mining Sandboxes''.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We totally agree. We changed the title of Section 3.3 and fixed this wrong mischaracterization related to our taint analysis usage, which is used not for mining sandboxes but rather as an alternative approach for identifying malware. Fixing this issue required modifications not only in Section 3.3 but also in many other parts of the paper (including the paper Title, Abstract, Introduction, and Results). Many thanks for raising this issue.}

@@

\vspace{0.2cm}

\item Also, FlowDroid requires as input the sources and sinks APIs. But you mine ``all sources and sinks 
paths''. Do you mean all APIs? FlowDroid will never finish running.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} You are right: we actually use a curate set of sensitive sources and sinks
  that is available in the FlowDroid repository.
  We changed Section 3.3 to clarify this point. Thanks once again.
  We hope that the current version of our paper fixes this problem.}

@@

\vspace{0.2cm}

\item The significance of this work is questionable. The first study is a mere replication of the existing
  work~\cite{DBLP:conf/wcre/BaoLL18}, except, disabling 
part of the framework. The finding is that DroidFax is important part for DroidXP. Well, your proved literature's correctness. 
It would be more impressive the other way round.

\vspace{0.2cm}

{\color{blue}{\bf Answer.} The relevance of replication in software engineer
  has gained much more attention in recent years~\cite{role-of-replication,shepperd-role-replication},
  not only to validate past results~\cite{msr-replication} but also to generate new insights
  from previous research results~\cite{kohl:icse-2020} or even refute past conclusions~\cite{toplas-replication}.
  Indeed, we carried out an external, non-exact replication
  of~\cite{DBLP:conf/wcre/BaoLL18}, and the results of our study
  shed light that the efficacy of the dynamic analysis tools is
  actually different from the previous report~\cite{DBLP:conf/wcre/BaoLL18}. That is,
  although we agree with the perspective of
  Shullet et al.~\cite{role-of-replication},
  who argue that an exact replication that achieves the same conclusions of an original work
  is still valuable to generalize the results of a research, here we go beyond that,
  and give evidence that the efficacy of the dynamic analysis tools in the previous research
  work had been overestimated. We review the introduction section to clarify this point.}

@@

\vspace{0.2cm}

{\color{blue}{\bf Answer.}The goal of the listings is twofold. First, to explain the characteristics of the malwares for which the mining sandbox approach could correctly identify the malicious behavior. Second, to highlight a particular kind of malwares for which the mining sandbox approach is not practical (last malware example). For the first class of malware, the malicious version of the apps frequently includes changes in the Android manifest file and also modifies the bytecode to include additional method calls that might share sensitive information. The listings show concrete examples of the code after a re-engineering effort, which might help readers understand why the mining sandbox approach works for those cases. Similarly, the last instance of malware only changes the manifest file. Since it does not include any additional method call, the mining sandbox approach could not point out the malicious version of the app as malware. We changed the last paragraphs of Section 4.1 to justify these listings better.
}

\vspace{0.2cm}

\item The title itself is inaccurate. You removed DroidFax from the replicated work~\cite{DBLP:conf/wcre/BaoLL18}.
  But it is not the only static analysis part. Actually, many dynamic testing tools use
  static analysis to better guide their testing strategy.

@@

\vspace{0.2cm}

\item ``The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the
analysis must often assume that additional behaviors are possible than actually would be.''
Please explain

\vspace{0.2cm}

{\color{blue}{\bf Answer.} We explained better this sentence in the second paragraph of our
  first section (Introduction). Thanks for raising this issue.}

### 2021-06-21 introduction.tex
changes in the RQs

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes\kn{The use of word same here makes me wonder if readers could be confused. IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right? Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which might lead to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and introduce a possible threat to the conclusions of that work.

>>>>

The same lack of understanding about the role of static analysis also appears in the work of Bao et al.~\cite{DBLP:conf/wcre/BaoLL18} (hereafter \blls), which presents an empirical study that compares different dynamic analysis tools for testing and mining Android sandboxes\kn{The use of word same here makes me wonder if readers could be confused. IMO the problem of how Static and dynamic analysis complement each other AND the role of static analysis in dynamic approaches are different (even if they sound similar), right? Reason I simply did not remove the word "same" is that I feel we need a bridge sentence here to make this transition of two similar sounding problems clear, because we only explore one of them.}. Their study leverages DroidFax~\cite{DBLP:conf/icsm/CaiR17a} to instrument $102$ pairs of Android apps (each pair comprising a benign and a malign version of an App) and to collect the information needed to mine sandboxes (that is, the calls to sensitive APIs).
Although the authors report a precision of at most 70\% of dynamic analysis tools to differentiate the benign and malicious versions of the apps, the authors ignore the fact that DroidFax statically analyzes the Android apps and also records calls to sensitive APIs (besides instrumenting the apps), which, as we discuss in this paper, leads to an overestimation of the performance of the dynamic analysis tools for mining sandboxes and might have introduced a possible threat to the conclusions of that work. Moreover, since DroidFax is an independent component (it is not part of the dynamic analysis tools explored in the \blls), a practitioner might run a dynamic analysis tool alone that is likely to present a smaller capacity to identify malware.

### 2021-06-21 setup.tex
changes in the RQs

\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis. a.k.a effect of taint analysis on sandboxes. But in the introduction we kind of use the general S-D interaction and this problem interchangeably. I have left a comment at the introduction.}
Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of {\bf dynamic analysis tools} for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured.
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

 \item What is the impact of the DroidFax static analysis algorithms into the results of the \blls?

 \item What is the effective performance of each test generation tool\kn{Should we use the term sandboxes instead of test generation tools? Test generation is just part of sandboxes right?}, in terms of the number of detected malware, when we
   discard the contributions of the DroidFax static analysis algorithms?

 \item What are the benefits of using taint
 analysis algorithms to complement the dynamic analysis approach for mining sandboxes?
\end{enumerate}

>>>>

\kn{Here it is extremely obvious and clear that we explore a very specific kind of interaction between static and dynamic analysis. a.k.a effect of taint analysis on sandboxes. But in the introduction we kind of use the general S-D interaction and this problem interchangeably. I have left a comment at the introduction.}
Our research work aims to better understand
the use of static analysis to mine Android sandboxes
and explore the benefits of combining taint analysis
with the mine sandbox approach for identifying malicious
behavior. 
On the one hand, Jamrozik et al. suggest that a 
static analysis approach for mining sandboxes
might be ineffective---due to \emph{overapproximation
problem}~\cite{DBLP:conf/icse/JamrozikSZ16The}.
However, to the best of our knowledge,
there is no empirical study comparing
static and dynamic analysis for mining sandboxes.
On the other hand, the \blls explored the mining sandbox approach by comparing
the performance of five {\bf dynamic analysis tools} (DroidMate, DroidBot, PUMA,
GUIRipper, and Monkey) for identifying
malicious behavior. Nonetheless, their
research also involved an external static analysis component (DroidFax)
whose impact on the results was not measured---in terms of malware
identification. 
This lack of understanding about the implications of
static analysis for mining sandboxes motivates
our research, which investigates the following research questions.

@@

\item What is the impact of the DroidFax static analysis algorithms on the results of the BLL-Study?
  We estimate the impact in terms of the number of detected malwares.

 \item What is the effective performance of each sandbox, in terms of the number of detected malware, when we
   discard the contributions of the DroidFax static analysis algorithms?

 \item What are the benefits of using taint
   analysis algorithms to complement the dynamic analysis approach for mining sandboxes,
   in terms of additional malwares identified?
\end{enumerate}
